Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-07 outputs/paper/paper.qmd
Updates to paper

temp_2002_2022 %>% filter(month_name == "Dec" | month_name == "Jan"| 
               month_name == "Feb" | month_name == "Mar") %>% ggplot(
              aes(x=year, y=max_temp, color=month_name)) + 
  geom_point() + labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

@@

temp_2002_2022 %>% filter(month_name == "Apr" | month_name == "May" | 
                            month_name == "Jun" | month_name == "Jul") %>% ggplot(
                              aes(x=year, y=max_temp, color=month_name)) + 
  geom_point() + labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

@@

temp_2002_2022 %>% filter(month_name == "Aug" | month_name == "Sep" | 
                            month_name == "Oct" | month_name == "Nov") %>% ggplot(
                              aes(x=year, y=max_temp, color=month_name)) + 
  geom_point() + labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

>>>>

level_order <- c("Dec", "Jan", "Feb","Mar")

temp_2002_2022 %>% filter(month_name == "Dec" | month_name == "Jan"| month_name == "Feb" | month_name == "Mar") %>% ggplot(aes(x=year, y=max_temp, color=factor(month_name, level = level_order))) + geom_point() + labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

@@

level_order <- c("Apr", "May", "Jun", "Jul")

temp_2002_2022 %>% filter(month_name == "Apr" | month_name == "May" | month_name == "Jun" | month_name == "Jul") %>% ggplot(aes(x=year, y=max_temp, color=factor(month_name, level = level_order))) + geom_point() + labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")

@@

level_order <- c("Aug","Sep", "Oct","Nov")

temp_2002_2022 %>% filter(month_name == "Aug" | month_name == "Sep" | month_name == "Oct" | month_name == "Nov") %>% ggplot(aes(x=year, y=max_temp, color=factor(month_name, level = level_order))) + geom_point() + labs(color="Month") + xlab("Year") + ylab("Maximum Temperature")
